---
title: "Issue 22"
output: github_document
---

> we would like to have the "Team" column from the root worksheet added to each stem similar to the date.

> Also, Harvard Forest would like to use the R code as well. Their data includes a "Sub_Quadrat" column on the root sheet of the workbook that currently doesn't populate like the "Team" column when running the code.

> I realize there will be little differences from site to site like this, so not sure how to avoid these issues going forward.

```{r setup, include=FALSE}
options(digits = 3)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  out.width = "70%",
  fig.align = "center",
  fig.height = 9,
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold"
)
```

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(fs)
  
  # install.packages("fgeo.tool")
  library(fgeo.tool)
  # devtools::install_github("forestgeo/fgeo.misc")
  library(fgeo.misc)
})

packageVersion("fgeo.tool")
packageVersion("fgeo.misc")
```

> I would like to export the files separately to complete the vetting process ... However, trying the xlff_to_xl function is writing the files as .NA instead of .xlsx.

Thanks! The file extensions should now be correct. The problem is a bug (I think) in the fs package (see https://github.com/r-lib/fs/issues/205).

(FYI, notice that the file extension is something you can change manually. Just rename the file to give it the correct extension; then the program associated to that extension should know how to open it.)

```{r}
input <- here(".buildignore/input")
dir_ls(input)

output <- here(".buildignore/issue_21/output")
xlff_to_csv(input, output, first_census = FALSE)

dir_ls(output)
```

> Can I use xlff_to_xl to write multiple files to one location?

Yes, as shown above. 

> Also, we would like to have the "Team" column from the root worksheet added to each stem similar to the date.

Okay (see https://github.com/forestgeo/fgeo.misc/issues/22)

