---
title: "Issue 21"
output: github_document
---

```{r setup, include=FALSE}
options(digits = 3)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  out.width = "70%",
  fig.align = "center",
  fig.height = 9,
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold"
)
```

Jess,

I downloaded the data (and removed the link).

From the two issues you mention, I think only one is actionable. 

* (not actionable) `xl_to_df()` does not exist in the package. Did it ever existed? I suspect that what you are trying to accomplish it already done by some of the `xlff_to_*()` variants. I have now made the [help file visible on the package website](https://forestgeo.github.io/fgeo.misc/reference/xlff_to_output.html). The examples section should clarify what these functions do.

* (actionable) I changed the code to not-fail when the column `tag` doesn't exist. I'm not sure why isn't there (although you may have explained)--I leave it to you to decide. Now the code produces output but there are a bunch of warnings that I encourage you to read and try to make sense of. See below:

```{r, error=TRUE}
library(purrr)
library(dplyr)
library(readr)
library(fs)
library(here)

# install.packages("fgeo.tool")
library(fgeo.tool)
# devtools::install_github("forestgeo/fgeo.misc")
library(fgeo.misc)

packageVersion("fgeo.tool")
packageVersion("fgeo.misc")

input <- here(".buildignore/issue_21/input")

# The input/ folder contains .xlsx file
dir_ls(input)

list_of_dataframes <- xlff_to_list(input, first_census = FALSE)
single_dataframe <- reduce(list_of_dataframes, bind_rows)

as_tibble(single_dataframe)

glimpse(single_dataframe)

# You can now save it as you please, for example, as a .csv
output <- here(".buildignore/issue_21/output/single_dataframe.csv")
write_csv(single_dataframe, path = output)

# The output/ folder now contains the file we just saved
dir_ls(path_dir(output))
```

